\documentclass{beamer}

% Recommended beamer themes:
% \usetheme{Madrid}        % Clean and modern
\usetheme{Berlin}        % Simple, with sidebar
% \usetheme{Frankfurt}     % Minimal, with top navigation
% \usetheme{CambridgeUS}   % Classic academic look
% \usetheme{Bergen}        % Elegant, with sidebar
% \usetheme{AnnArbor}      % Colorful, with sidebar
% \usetheme{Darmstadt}     % Professional, with sidebar
% \usetheme{Singapore}     % Clean, with sidebar
% \usetheme{Warsaw}        % Modern, with navigation bar


% 图形与排版支持
\usepackage{graphicx}       % 图形插入支持
\usepackage{adjustbox}      % 高级图片调整
\usepackage{framed}         % 边框环境
\usepackage{amssymb,amsfonts} % 数学符号和字体支持
% \usepackage{amsthm}         % 定理环境支持
\usepackage[dvipsnames]{xcolor} % 颜色支持
\usepackage[most]{tcolorbox} % 彩色盒子环境
\usepackage{tikz}           % 矢量绘图
\usepackage{tikz-cd}        % 交换图绘制
\usepackage[all]{xy}        % 交换图绘制
%%
% \usepackage{enumitem}       % 自定义列表标签
%%

\usepackage[backend=biber,style=alphabetic]{biblatex} % 参考文献管理
\addbibresource{ref.bib}

\usepackage[nameinlink]{cleveref} % 智能引用（自动添加前缀）

% 定理环境定义
\newtheorem{conjecture}{Conjecture}
\newtheorem{question}{Question}
% \newtheorem{definition}{Definition}

% 中文支持
\usepackage[scheme=plain]{ctex} % 中文基础方案
\usepackage{fontspec}      % 字体配置

% Unicode数学字体支持
\usepackage{unicode-math}
\setmainfont{Times New Roman}
\setmathfont{Cambria Math}
\setmathfont{STIX Two Math}[range=cal]
\setmathfont{Libertinus Math}[range=scr]

\input{notation.tex}

% \usepackage{mathabx,epsfig}
\def\acts{\ \rotatebox[origin=c]{-90}{$\circlearrowright$}\ }
\def\racts{\ \rotatebox[origin=c]{90}{$\circlearrowleft$}\ }
\def\dacts{\ \rotatebox[origin=c]{0}{$\circlearrowright$}\ }
\def\uacts{\ \rotatebox[origin=c]{180}{$\circlearrowright$}\ }

\title{Dynamical Iitaka Theory on Fano Contractions}
\author{Tianle Yang, \\ joint work with Sheng Meng and Long Wang}
\date{2026.01.07}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

% \begin{frame}{Outline}
%     \tableofcontents
% \end{frame}


\section{Algebraic Dynamics}

\begin{frame}{Algebraic Dynamics}
    We work over an algebraically closed field \(\kkk\) of characteristic zero, usually \(\kkk=\bbC\) or \(\kkk=\overline{\bbQ}\).

    \pause

    The fundamental objects in algebraic dynamics are \((X,f)\), where \(X\) is a variety and \(f:X \dashrightarrow X\) is a dominant rational self-map.

    Here we focus on the case \(X\) is projective and \(f\) is a surjective endomorphism.

    For simplicity, we assume that \(X\) is smooth.
\end{frame}

\begin{frame}{Dynamical degree and arithmetic degree}

    \begin{definition}[First dynamical degree]\label{def: delta_f}
        The \textit{first dynamical degree} \(\delta_f\) of \(f\) is defined to be the following limit
        \[
        \delta_f := \lim_{n\to\infty}((f^n)^*H\cdot H^{\dim X-1})^{1/n}\in\mathbb{R}_{\geq 1},
        \]
        where $H$ is an ample Cartier divisor on \(X\).
    \end{definition}

    % In our case, 
    % it is also known that 
    % the first dynamical degree \(\delta_f\) coincides with the spectral radius of the induced linear operation \(f^*|_{\textup{NS}(X)\ten_\bbZ \bbC}\).

    \begin{definition}[Arithmetic degree]\label{def: alpha_f}
        Let \(h:X(\overline{\bbQ}) \to \bbR\) be the height function associated to an ample divisor on \(X\).
        Then for every \(x\in X(\kkk)\), we define the \emph{arithmetic degree of \(f\) at \(x\)} by
        \[
            \alpha_f(x)=\lim_{n\to\infty} \max\{h(f^n(x)),1\}^{1/n} \in \mathbb{R}_{\geq 1}.
        \]
    \end{definition}
\end{frame}

% \begin{frame}{Arithmetic degree}

%     Assume that \(\kkk = \overline{\bbQ}\).
%     Then we can define a \emph{height function}
%     \[ h: X \subset \bbP^N \to \bbR \]
%     which measures the arithmetic complexity of \(\kkk\)-points.

%     For example, \(x = [x_0:\cdots:x_n]\in \bbP^N_\bbQ\) with \(x_i\in \bbZ\) and \(\gcd(x_0,\ldots,x_n)=1\), then
%     \[ h(x) = \log \max\{|x_0|,\ldots,|x_n|\}. \]
    



% \end{frame}


\begin{frame}
    \frametitle{KSC}
        
    \begin{conjecture}[{Kawaguchi-Silverman Conjecture $=$ KSC}]\label{conj: ksc} 
        Let $x \in X(\kkk)$, and suppose that the (forward) orbit $O_f(x) = \{f^n(x)\, |\, n\ge 0\}$  is Zariski dense in $X$.
        Then the arithmetic degree at $x$ is equal to the dynamical degree of $f$, i.e.,
        $\alpha_f(x) = \delta_f$.
    \end{conjecture} 

    \pause

    If we have an equivariant surjective \((X,f) \dashrightarrow (Y,g)\) such that \(\delta_f = \delta_g\), 
    then KSC for \((Y,g)\) implies KSC for \((X,f)\).

\end{frame}

% \begin{frame}
%     \frametitle{Fibration on algebraic geometry}

%     \begin{definition}
%         A \emph{fibration} is a dominant rational map \(\pi: X \dashrightarrow Y\) with connected fibers between normal projective varieties.
%     \end{definition}

% \end{frame}


\begin{frame}
    \frametitle{Fibration on algebraic dynamics}

    % \begin{definition}
    %     A fibration \(\pi: X \dashrightarrow Y\) is said to be \emph{\(f\)-equivariant} if there is a dominant rational map \(g: Y \dashrightarrow Y\) such that \(\pi \circ f = g \circ \pi\).
    % \end{definition}

    A fibration \(\pi: X \dashrightarrow Y\) is said to be \emph{\(f\)-equivariant} if there is a dominant rational map \(g: Y \dashrightarrow Y\) such that \(\pi \circ f = g \circ \pi\).

    \pause

    Suppose that the fibration \(\pi:X \to Y\) is given by a semiample line bundle \(L\).
    If \(f^*L \sim qL\) for some \(q\geq 1\), 
    then \(\pi\) is \(f\)-equivariant by the rigidity lemma and simple intersection theory.

    \pause

    What about the case when \(L\) is only effective or when \(f^*L\) is not proportional to \(L\)?

\end{frame}


\section{Dynamical Iitaka Theory}

\begin{frame}{Dynamical Iitaka dimension}

    
    \begin{definition}[Dynamical Iitaka dimension]
        Let \(D\) be a Cartier divisor on \(X\).
        The {\it dynamical $f$-Iitaka dimension} of $D$ is defined as 
        $$\kappa_f(X,D):=\max\{\kappa(X,D')\,|\,D'=\sum_{i=0}^m a_i (f^*)^iD, a_i\in\bbZ\}.$$
    \end{definition}
\end{frame}

\begin{frame}{Dynamical Iitaka fibration}

    \begin{theorem}[{ref. \cite[Theorem 4.6]{MZ23b}}]
        Suppose that $\kappa_f(X,D)\ge 0$.
        Then there is an $f$-equivariant dominant rational map 
        \[ f \acts X \dashrightarrow Y \racts f|_Y \]
        with \(Y\) normal projective of dimension \(\kappa_f(X,D)\) and \(f|_Y\) a surjective endomorphism.
    \end{theorem}
\end{frame}


\begin{frame}
    \frametitle{The ramification divisor}

    The \emph{ramification divisor} \(R_f\) is defined by 
    \[ R_f := \sum_{E} (\operatorname{mult}_E f^*(f(E)) - 1) E \]
    where the sum runs over all prime divisors \(E\) of \(X\).

    It is effective and satisfies the ramification formula
    \[ K_X = f^*K_X + R_f. \]

\end{frame}


\begin{frame}{Dynamical Iitaka Program for ramification divisor}

    We consider three situations of $\kappa_f(X,R_f)$ and briefly introduce how the dynamical Iitaka theory works.
    
    \pause

    \begin{itemize}
        \item $\kappa_f(X,R_f)=0$. 
            Then $f^{-1}(\Supp R_f)=\Supp R_f$ and the restriction $$f|_{X\backslash \Supp R_f}\colon X\backslash \Supp R_f\to X\backslash \Supp R_f$$ is (quasi-)\'etale.
        
        \pause
        
        \item $0<\kappa_f(X,R_f)<\dim X$.
            We then have an $f$-equivariant dominant rational map
            $$\varphi_{f,R_f}\colon X\dashrightarrow Y$$
            with $0<\dim Y=\kappa_f(X,R_f)<\dim X$.

        \pause

        \item $\kappa_f(X,R_f)=\dim X$. 
            In this case, $R_{f^s}$ is big when $s\gg 1$.
    \end{itemize}

\end{frame}

\section{About our paper}


\begin{frame}
    \frametitle{Settings}

    We consider the case the \((X,f)\) has admitted an \(f\)-equivariant extremal Fano contraction \(\pi: X \to Y\) such that \(\delta_f > \delta_{f|_Y}\).

    \pause

    Since \(\pi\) is of relative Picard number 1, the general fiber \(X_y\) is Fano and \(\delta_f > \delta_{f|_Y} \geq 1\), the ramification divisor \(R_f\) is non-trivial and \(\pi\)-ample.

    \pause

    Hence we want to use the dynamical Iitaka fibration associated to \(R_f\) to get another \(f\)-equivariant fibration.

    \pause

    Further assume that the base \(Y\) is either an abelian variety or a smooth projective variety of Picard number one, we get our main results.

\end{frame}


\begin{frame}
    \frametitle{Main Results}

    \begin{theorem}\label{mainthm: abelian}
        Let $f$ be a surjective endomorphism of a smooth projective variety $X$ admitting an extremal Fano contraction $\pi:X\to Y$ to an abelian variety $Y$ of positive dimension.
        Suppose $f$ admits a Zariski dense orbit and $\delta_f>\delta_{f|_Y}$.
        Then the following hold.
        \begin{enumerate}
            \item The ramification divisor satisfies $f^*R_f\equiv \delta_f R_f$.
            \item There exists an $f$-equivariant dominant rational map $\varphi:X\dashrightarrow Z$, 
            which is the $f$-Iitaka fibration of $R_f$, 
            such that $0<\dim Z<\dim X$ and $f|_Z$ is $\delta_f$-polarized.
        \end{enumerate}
    \end{theorem}

\end{frame}

\begin{frame}
    \frametitle{Main Results}

    \begin{theorem}\label{mainthm: rho1}
        Let $f$ be a surjective endomorphism of a smooth projective variety $X$ admitting an $f$-equivariant {\bf smooth} extremal Fano contraction $\pi:X\to Y$ with $\rho(Y)=1$.
        Suppose $\delta_f>\delta_{f|_Y}=1$.
        Then the following hold.
        \begin{enumerate}
            \item The ramification divisor satisfies $f^*R_f\equiv \delta_f R_f$.
            \item There exists an $f$-equivariant dominant rational map $\varphi:X\dashrightarrow Z$, 
            which is the $f$-Iitaka fibration of $R_f$, 
            such that $0<\dim Z<\dim X$ and $f|_Z$ is $\delta_f$-polarized.
        \end{enumerate}
    \end{theorem}

\end{frame}

\begin{frame}
    \frametitle{Main Results}

    \begin{corollary}\label{maincor: abelian}
        KSC holds for any smooth projective variety $X$ admitting an extremal Fano contraction to an abelian variety. 
    \end{corollary}


    \begin{corollary}\label{maincor: pn}
        KSC holds for any $\mathbb{P}^n$-bundle over either a $Q$-abelian variety or a smooth projective variety of Picard number one. 
    \end{corollary}

\end{frame}




\end{document}